Predicting Conflict Escalation

### 2023-04-29 docs/hes_final/article.qmd
embed images written by figs.ipynb

TODO: Table (for numerical metrics) and plots (for roc_auc) for 2 models

@@

TODO: map comparison images

>>>>

![Model performance metrics](imgs/tbl-best-max-metrics.png){width=50%}

![Model performance metrics](imgs/tbl-best-min-metrics.png){width=50%}

![Receiver Operator Characteristics](imgs/fig-roc.png){width=50%}

![Precision Recall Curve](imgs/fig-prc.png){width=50%}

@@

![Predictions for 2023-01 from transformer model](imgs/fig-y_pred_proba-transformer-202301.png){width=50%}

![Predictions for 2023-01 from xgboost model](imgs/fig-y_pred_proba-xgboost-202301.png){width=50%}

![Predictions for 2023-01 from ffnn model](imgs/fig-y_pred_proba-ffnn-202301.png){width=50%}
